---
title: "NOAA_Earthquake_Analyzer"
author: "Sanjaya J Shetty"
date: "29 October 2021"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{About NOAA}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

The package 'NOAA_Earthquake_Analyzer' is used to clean, manipulate and visualize the NOAA dataset

### Installing the package

To install the package, you must be having 'devtools' package.

```{r, eval=FALSE}
install.packages('devtools') # installing devtools

devtools::install_github('SanjayShetty01/NOAA_Earthquake_Analyzer')
```

### Loading the Required Packages

```{r, warning=FALSE,message=FALSE}
library(NoaaEarthquakeAnalyzer)
library(readr)
library(ggplot2)
library(readr)
library(dplyr)
library(magrittr)
```
## Load and Cleaning the data 

use data(earthquakes) to load the data into the environment. If you want to visualize a data stored in your local system, use `eq_load_data` function to load the tsv data (from the NOAA website) onto the environment. 

```{r}
data = NoaaEarthquakeAnalyzer::earthquakesdata



cleanedData =  eq_clean_data(data)
   
```    

## Visualzing the timeline plot of the Data 

Columns required for the geom_time()

* `x = DATE`
* `y = COUNTRY`
* `color = TOTAL_DEATHS`
* `size = EQ_PRIMARY`


```{r}
cleanedData %>%

            filter(COUNTRY %in% 'ITALY',
                                 Year >= 1000 &
                                 Year <= 2000) %>% 
            ggplot(.,aes(x = DATE, 
                          y = COUNTRY, 
                          color = `Total Deaths`,
                          size = Mag))+
            geom_timeline() 
              
```

## Creating Leaflet map 

The user could use eq_create_label to have a HTML formatted label, which would give addition information. 

```{r}

data %>% 
  eq_clean_data(.) %>%  
  dplyr::filter(COUNTRY == "ITALY" )%>%   
  dplyr::mutate(popup_text = eq_create_label(.)) %>% 
  eq_map(annot_col = "popup_text")

```

```{r}
data %>%
eq_clean_data() %>% 
  dplyr::filter(lubridate::year(DATE) >= 1855) %>% 
  eq_map(annot_col = "DATE")
```
